Statically Typed String Sanitation Inside a Python

### 2014-08-18 sanitation-psp14/sanitation-psp14-short.tex
Finished trivial edits.

\begin{thm}[Type Safety for the String Fragment of $\lambdas$.] \label{thm:scorrect}
  If $\sctx \vdash e : \stringin{r}$ 
  then $e \sreduces \rstr{s}$ and $\sctx \vdash \rstr{s} : \stringin{r}$.
\end{thm}
\begin{proof}
By induction on the typing relation.
The S-T-Concat case requires Lemma \ref{thm:regexprops} 
and the S-T-Replace case appeals to Lemma \ref{thm:substcorrespondence}.
\end{proof}

@@

\begin{thm}[Correctness of Input Sanitation for $\lambdas$.]\label{thm:scorrect}
  If  $\sctx \vdash e : \stringin{r}$ and $e \sreduces \rstr{s}$ then $s \in \lang{r}$.
\end{thm}
\begin{proof}
  Follows directly from type safety, canonical forms for $\lambdas$.
\end{proof}

@@

\begin{thm}[Translation Correctness.] \label{thm:tcorrect}
If $\sctx \vdash e : \stringin{r}$ then there exists a $\iota$ such that $\trden{e} = \iota$, 
$\iota \treduces \tstr{s}$, and $e \sreduces \strin{s}$.
\end{thm}

>>>>

\begin{thm}[Type Safety for the String Fragment of $\lambdas$.] \label{thm:scorrect}
  If $\sctx \vdash e : \sigma$ 
  then $e \sreduces e'$ and $\sctx \vdash e' : \stringin{r}$.
\end{thm}
\begin{proof}
By induction on the typing relation.
The S-T-Concat case requires Lemma \ref{thm:regexprops} 
and the S-T-Replace case appeals to Lemma \ref{thm:substcorrespondence}.
\end{proof}

\begin{thm}[Canonical Forms for String Fragment of $\lambdas$.]\label{thm:cfs}
  If $\sctx \vdash e : \stringin{r}$ 
  then $e \sreduces \rstr{s}$ 
\end{thm}

@@

\begin{thm}[Correctness of Input Sanitation for $\lambdas$.]\label{thm:scorrect}
  If  $\sctx \vdash e : \stringin{r}$ and $e \sreduces \rstr{s}$ then $s \in \lang{r}$.
\end{thm}
\begin{proof}
  Follows directly from type safety, canonical forms for $\lambdas$, and inversion of the typing relation for $\lambdas$.
\end{proof}

@@

\begin{thm}[Translation Correctness.] \label{thm:tcorrect}
If $\sctx \vdash e : \stringin{r}$ then there exists an $\iota$ such that $\trden{e} = \iota$, 
$\iota \treduces \tstr{s}$, and $e \sreduces \strin{s}$.
\end{thm}
